%        File: writeup.tex
%     Created: Wed Oct 05 10:00 AM 2011 P
% Last Change: Wed Oct 05 10:00 AM 2011 P
%
\documentclass[a4paper]{article}
\usepackage{listings}
\usepackage{color}
\usepackage{textcomp}
\usepackage{program}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
   backgroundcolor=\color{lbcolor},
   tabsize=3,
   % rulecolor=,
   language=Java,
   basicstyle=\scriptsize,
   % upquote=true,
   % aboveskip={1.5\baselineskip},
   columns=fixed,
   % showstringspaces=false,
   % extendedchars=true,
   breaklines=true,
   % prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
   % frame=single,
   % showtabs=false,
   % showspaces=false,
   % showstringspaces=false,
   % identifierstyle=\ttfamily,
   keywordstyle=\color[rgb]{0,0,1},
   commentstyle=\color[rgb]{0.133,0.545,0.133},
   stringstyle=\color[rgb]{0.627,0.126,0.941},
} 
\newcommand{\sourceRoot}{../src/}
\newcommand{\myPackage}{}
\newcommand{\myJPackage}{}
\newcommand{\sourcePackage}[2]{  \subsection*{Package: #2}
                                 \renewcommand{\myPackage}{#1}
                                 \renewcommand{\myJPackage}{#2}}
\newcommand{\sourceClass}[1]{    \lstinputlisting[caption=\myJPackage.#1]
                                 {\sourceRoot\myPackage/#1}}
\begin{document}
\title{The Solving of the Simple Single Player Game Involving Sliding
Blocks}
\author{Zachary M. Bush}
\maketitle
\tableofcontents
\lstlistoflistings
\newpage
\section{The Plan}
\subsection{Checking For Goal Configuration}
In this section we will simply discuss the plan for implementing the blocks 
project. The basis of this algorithm will be to look through the list of the 
goal orientation. For each goal position, look through the list of current 
block positions and check if there is a block that is of the correct size and 
in that position. 
\begin{lstlisting}[caption=Checking for Goal Configuration]
boolean isCorrect(Block [] currentBlocks, Block [] goalBlocks){
   for(int i = 0; i < goalBlocks.length; i++){
      boolean found = false;
      for(int j = 0; j < currentBlocks.length; j++){
         if(goalBlocks[i].equals(currentBlocks[j])){
            found = true;
            break;
         }
      }
      if(!found){
         return false; // If we haven't matched one of the goal blocks. 
                       // Then the goal is not reached
      }
   }
   return true;
}
\end{lstlisting}
\subsection{Generate Possible Moves}
To generate possible moves, we will need to look at each block individually. 
For each block we need to look to the left and right for open spots, and 
compare the number of open spots to the height of the block. If it is greater 
than or equal to the height, then that is a possible move. (we will only 
consider moving blocks one position at a time, to simplify the generation 
process). The process then needs to be repeated for the above and below 
comparing against the width. 
\begin{lstlisting}[caption=Generate Possible Moves]
Move [] possibleMoves(Block [] currentBlocks){
   boolean occupiedBlocks[][] = new boolean[width][height];
   // Set initial values to false.
   for(i = 0; i < currentBlocks.length; i++){
      for(x = 0; x < curentBlocks[i].width; x++){
         int xpos = currentBlocks[i].x;
         int ypos = currentBlocks[i].y;
         for(y = 0; y < currentBlocks[i].height; y++){
            occupiedBlocks[x + xpos][y + ypos] = true;
         }
      }
   }
   for(i = 0; i < currentBlocks.length; i++){
      Block b = currentBlock[i];
      boolean valid = true;
      if(b.y > 0){
         for(int x = 0; x < b.width; x++){
            if(!occupiedBlocks[b.x+x][b.y-1]){
               valid = false;
               break;
            }
         }
      }
   }
   // Repeat the process for left, right, and below. 
}
\end{lstlisting}

\subsection{Decide what to do next}
To decide which of the generated moves to use, we will simply choose the first 
one in the list that hasn't yet been seen (this mechanism will be discussed in 
subsection \ref{ssec:checkDup}), and try it. In future we may define a delta 
function to chose the move that is ``closest'' to the goal (this may increase 
efficiency).

\subsection{Make and Unmake moves}
Making and unmaking moves is fairly simple. There are two ways I can see to try 
doing it: 
\begin{enumerate}
\item Create a copy of the board to make the move, and then unmaking would be 
      just using the unmodified version.  (not memory efficient)
\item Create a ``move'' procedure that takes a start position and a goal 
      position. With that, we can use move(from, to) to make the move and use 
      move(to, from) to unmake it. 
\end{enumerate}

\subsection{Detect Previously Visited configurations}
With the class storing the state of the board, add a hashing function to allow 
us to put it into a hashtable and later look it up. This is a place where some 
optimizations could be done, but to get the code working, we will just convert 
the board to a string and hash that string, using string's hashing function. 
\label{ssec:checkDup}


\sourcePackage{edu/berkeley/eecs/inst/zipcodeman/blocks}
		      {edu.berkeley.eecs.inst.zipcodeman.blocks}
\sourceClass{Solver.java}
\sourceClass{Board.java}
\sourceClass{Block.java}
\sourceClass{Reporting.java}
\sourceClass{Move.java}
\sourceClass{R.java}


\end{document}


